MS_Intro_Short

### 2023-01-29 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
minor tweaks

In this paper, we introduce a framework for developing the ready4 MOSHEM. Specifically we:

(i) describe a framework that is comprised of:
  - a set of standards for implementing a MOSHEM; and
  - a modelling toolkit (repositories and software) to author MOSHEM modules, supply them with data and undertake reproducible analyses consistent with those standards.

>>>>

In this paper, we:

(i) describe a framework comprised of:
  - a set of standards for implementing an accountable, reusable and updatable MOSHEM; and
  - a modelling toolkit (online repositories and software) for applying those standards to the authoring of ready4 modules, datasets and analyses.

### 2023-01-29 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
minor tweaks

In this article we introduced a framework that we developed to help us implement ready4 - a MOSHEM in youth mental health. We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we for applying those standards to the development and use of ready4. We also provided an overview of an initial set of ready4 modules that we developed with the framework and which we applied to implement a utility mapping study in a clinical mental health sample of young people. We reviewed the modules, datasets and analyses generated by that study against framework standards.

The strengths. limitations and issues raised by this work can be discussed in terms of relevance to future development of the ready4 MOSHEM, to health economists interested in undertaking other MOSHEMS and to funders of health economic research.

## Implications for the development of the ready4 MOSHEM
Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].

One of the main novel contributions of the framework we have developed is that it declares an explicit set of standards for the implementation and use of a MOSHEM. Standardisation is an essential enabler of workflow automation, module interoperability, and transferability of methods<!-- and efficient collaboration  -->. The framework's modelling toolkit has enabled us to partially automate workflows for authoring, documenting and disseminating ready4 modules, datasets and analyses. The modelling toolkit's practical utility has been demonstrated through its application in creating all ready4 components used in a utility mapping study [@Hamilton2021.07.07.21260129] and the automation it facilitates makes the development and curation of a large and growing number of ready4 digital assets more tractable. The interoperability of the ready4 modules we have developed today is demonstrated in multiple example literate programs on the ready4 documentation website [@rfwn2022] and in the program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906].

@@

>>>>

In this article we introduced a framework that we developed to help us implement ready4 - a MOSHEM in youth mental health. We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we created for applying those standards to the development and use of ready4. We also provided an overview of an initial set of ready4 modules developed with the framework to implement a utility mapping study. We reviewed the modules, datasets and analyses generated by that study against framework standards.

The strengths, limitations and issues raised by this work can be discussed in terms of relevance to future development of ready4, to health economists interested in undertaking other MOSHEMS and to funders of health economic research.

## Implications for the development of the ready4 MOSHEM
One of the main novel contributions of the framework we have developed is that it declares an explicit set of standards for the implementation and use of a MOSHEM. A practical benefit of specifying these standards is that it enabled us to develop a modelling toolkit to partially automate workflows for authoring, documenting and disseminating ready4 modules, datasets and analyses. The modelling toolkit's practical utility has been demonstrated through its application in creating all ready4 components used in a utility mapping study [@Hamilton2021.07.07.21260129] and the automation it facilitates makes the development and curation of a large and growing number of ready4 digital assets more tractable. The interoperability of the ready4 modules we have developed today is demonstrated in multiple example literate programs on the ready4 documentation website [@rfwn2022] and in the program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906].

@@

Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].

### 2023-01-29 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
minor tweaks

We are developing ready4, a modular OSHEM (MOSHEM) on the mental health of young people aged 12 to 25 that we are initially applying to four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
<!-- There is therefore an opportunity for health economists to undertake mental health research of significant potential public benefit. -->

@@

Standardisation is an essential enabler of workflow automation, module interoperability, and transferability of methods<!-- and efficient collaboration  -->.

>>>>

We are developing ready4 (https://www.ready4-dev.com), a modular OSHEM (MOSHEM) on the mental health of young people aged 12 to 25. We are initially applying ready4 to four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
<!-- There is therefore an opportunity for health economists to undertake mental health research of significant potential public benefit. -->

@@

To undertake this work we first needed to develop a framework for standardisation. Standardisation is an essential enabler of automation, collaboration, interoperability and transferability in modular and open source approaches. However, MOSHEMs remain rare and is unclear what standards are most appropriate to specify. A MOSHEMs is a computational modelling project, so standards developed for ready4 will need to be verified and implemented by software, some of which will need to be developed for this specific purpose.
